A Bayesian model for the K2 data

### 2014-04-28 text/prob_model/prob_model.tex

Taking this together we calculate, for each critical condition $k$ a
target probability vector $\myvec{t}^k =
\tuple{t^k_{\text{lit}},t^k_{\text{loc}},t^k_{\text{glb}},t^k_{\text{err}}}$
with which we expect an answer to be classified as LIT, LOC, GLB or as
an error. For example, for AS-N, where LIT can be judged before GLB
before LOC, we get:
\begin{align*}
  t^{\text{as-n}}_{\text{lit}} & \propto q \
  p^\text{as-n}_{\text{lit}} + e^\text{as-n} &   t^{\text{as-n}}_{\text{loc}} & \propto (1-q)^2 \
  p^\text{as-n}_{\text{loc}} + e^\text{as-n} \\
  t^{\text{as-n}}_{\text{glb}} & \propto (1-q) \
  p^\text{as-n}_{\text{glb}} + e^\text{as-n} &   t^{\text{as-n}}_{\text{err}} &
  \propto 12 e^\text{as-n}
\end{align*}
Two remarks. The vector $\myvec{t}^k$ should be normalized eventually,
which is why $\propto$ is used instead of $=$. Also, the probability
of error $t^{\text{as-n}}_{\text{err}}$ comes from the observation
that there are 15 positions in total in an AS-sequence at which
subjects can make an erroneous choice, but we have accounted for three
of these already as adding to the count of answers indicative of
relevant readings.

>>>>

Taking this together we calculate, for each critical condition $k$ a
target probability vector $\myvec{t}^k =
\tuple{t^k_{\text{lit}},t^k_{\text{loc}},t^k_{\text{glb}},t^k_{\text{err}}}$
with which we expect an answer to be classified as LIT, LOC, GLB or as
an error. For example, for AS-N, where LIT can be judged before GLB
before LOC, we get:
\begin{align*}
  t^{\text{as-n}}_{\text{lit}} & \propto q \
  p^\text{as-n}_{\text{lit}} + e^\text{as-n} &   t^{\text{as-n}}_{\text{loc}} & \propto (1-q)^2 \
  p^\text{as-n}_{\text{loc}} + e^\text{as-n} \\
  t^{\text{as-n}}_{\text{glb}} & \propto (1-q)q \
  p^\text{as-n}_{\text{glb}} + e^\text{as-n} &   t^{\text{as-n}}_{\text{err}} &
  \propto 12 e^\text{as-n}
\end{align*}
Two remarks. The vector $\myvec{t}^k$ should be normalized eventually,
which is why $\propto$ is used instead of $=$. Also, the probability
of error $t^{\text{as-n}}_{\text{err}}$ comes from the observation
that there are 15 positions in total in an AS-sequence at which
subjects can make an erroneous choice, but we have accounted for three
of these already as adding to the count of answers indicative of
relevant readings.
